\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-12 paper/ms.tex
adding discussion of model selection and example

In any application of \celerite~--~or any other GP model, for that
matter~--~one must choose a kernel.
A detailed discussion of how to choose a kernel is beyond the scope of this
paper and the interested reader is directed to Chapter~5 of
\citet{Rasmussen:2006} a general introduction, but we include a summary and
some suggestions specific to \celerite\ here.
We argue that the most satisfying method of choosing a kernel is to use
physical motivation and the discussion in \sect{sho} provides an opportunity
for justified model specification when \celerite\ is applied to parameter
estimation from stellar light curves.
However, it is not always possible to rely on physics to specify the model
and, in these cases, it is useful to have other tools at one's disposal.
One option is to compute the evidence integral or Bayes factor for a set of
models and choose the model with the highest evidence.
Another option is to perform cross validation and select the model with the
best predictive performance.
For continuous autoregressive moving average models (we return to these in
\sect{compare}), \citet{Kelly:2014} recommend the Bayesian Information
Criterion (BIC) as a method for selecting the order of the model.
This is a total hack, but I guess that you could do it if you wanted.

@@

@@

>>>>

In any application of \celerite~--~or any other GP model, for that
matter~--~we must choose a kernel.
A detailed discussion of model selection is beyond the scope of this paper and
the interested reader is directed to Chapter~5 of \citet{Rasmussen:2006} an
introduction in the context of GPs, but we include a summary and some
suggestions specific to \celerite\ here.

For many of the astrophysics problems that we will tackle using \celerite, it
is possible to motivate the kernel choice physically.
We give three examples of this in the next section and, in these cases, we
have a physical description of the system that generated our data, we
represent that system as a \celeriteterm\ model, and use \celerite\ for
parameter estimation.
For other projects, we might be interested in comparing different theories
and, in those case, we would need to perform formal model selection.

Sometimes, it is not possible to choose a physically motivated kernel when we
use a GP as an effective model.
In these cases, we recommend starting with a mixture of stochastically-driven
damped SHOs (as discussed in \sect{sho}) and select the number of oscillators
using Bayesian model comparison, cross-validation, or another model selection
technique.
Despite the fact that it is less flexible than a general \celeriteterm\
kernel, we recommend the SHO model in most cases because it is 1-time mean
square differentiable
\begin{eqnarray}
\left.\frac{\dd k_\mathrm{SHO}(\tau)}{\dd \tau}\right|_{\tau=0} = 0 \quad,
\end{eqnarray}
giving smoother functions than the general \celeriteterm\ model that is only
mean square continuous.

For a similar class of models~--~we return to these below in
\sect{compare}~--~\citet{Kelly:2014} recommend using an ``information
criterion'', such as the Akaike information criterion (AIC) or the Bayesian
information criterion (BIC), as a model selection metric.
These criteria are easy to implement and we use the BIC in \sect{example2}
but, since are only formally valid under specific sets of assumptions, we
cannot recommend their use in general.

@@

We choose this functional form by comparing the Bayesian information criterion
(BIC) for a set of different models.
In each model, we take the sum or product of $J$ SHO terms, find the maximum
likelihood model using \project{L-BFGS-B} and compute the BIC
\citep{Schwarz:1978}
\begin{eqnarray}
\mathrm{BIC} = -2\,\mathcal{L}^* + K\,\log N
\end{eqnarray}
where $\mathcal{L}^*$ is the value of the likelihood at maximum, $K$ is the
number of parameters, and $N$ is the number of data points.
\Figure{bic} shows the value of the BIC for a set of products and sums of SHO
terms and the model that we choose has the lowest BIC.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/simulated/bic.pdf}
\caption{\response{
    The Bayesian information criterion (BIC) evaluated for the data from
    \Figure{simulated-wrong} and different kernel choices.
    The $x$-axis shows the number of terms included in each model.
    The blue circles show models where the terms have been summed and the
    orange squares indicate that the model is a product of terms.
    In the product models, the parameters $S_0$ and $Q$ are held fixed at $1$
    and $1/\sqrt{2}$ respectively for all but the first term.
    The dashed black line shows the minium value of the BIC and this
    corresponds to the model chosen in the text.}
    \figurelabel{bic}}
\end{center}
\end{figure}
